---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rwRtools

<!-- badges: start -->
<!-- badges: end -->

The goal of rwRtools is to make it easy to access The Lab's datasets and get started with research. 

TODO: big up the lab, links to RW etc

## Installation

You can install rwRtools from GitHub like so:

``` r
devtools::install_github("RWLab/rwRtools", dependencies = TRUE)
```

## Demo

Authorise a Google Identity to access The Lab's cloud infrastructure by doing:

```{r auth example}
# install and load required packages inc. dependencies  , eval=FALSE, echo=TRUE
if(!require("pacman")) install.packages("pacman")
pacman::p_load_gh("RWLab/rwRtools", dependencies = TRUE)

rwlab_gc_auth()
```

You will be prompted to select a Google Identity in a browser and the copy and paste an authentication code back at the call site.
