---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rwRtools

<!-- badges: start -->
<!-- badges: end -->

The goal of `rwRtools` is to make it easy to access The Lab's datasets and get started with research. 

## What is The Lab?

The Lab is [Robot Wealth's](https://robotwealth.com/) portal for collaborative research. 

It is organized around **Research Pods,** which contain data, ideas, research and peer-reviewed edges for a given market question.

For example:

- in the *Equity Factor Research Pod* we look at the question: "*What factors predict the relative performance of stocks in the Russell 1000 index?"*
- In the *Global Risk Premia Research Pod* we look at the question: "*What is the most effective way to get paid for taking on global market risks?* "

## What is the purpose of The Lab?

**The Lab serves three purposes:**

1. It gets you hands-on with the research effort. As well as contributing, you'll learn a ton in the process. 
2. It scales the research effort by enabling community contribution.
3. It makes the fruits of that scaled research effort available to the entire community.

## Demo

### Install and load

The easiest way to install and load `rwRtools` and its dependencies is via the `pacman` library:

```{r}
if(!require("pacman")) install.packages("pacman")
pacman::p_load_gh("RWLab/rwRtools", dependencies = TRUE)
```

If you prfer, you can also use `devtools` to install:

```{r, eval=FALSE, echo=TRUE}
devtools::install_github("RWLab/rwRtools", dependencies = TRUE)
```


### Quickstart: Set up for working on a Research Pod

After installing and loading `rwRtools`, this is the quickest way to set up a session for working on a particular Research Pod.

```{r, eval=FALSE, echo=TRUE}
setup_for_pod(pod = "EquityFactors", path = ".")
```

This kicks off the OAuth process and if successful, transfers all objects associated with the Pod from GCS to `path`. 

If your session is interactive, you will be prompted in a browser to select a Google Identity and copy and paste an authentication code back at the call site.

### List The Lab's Research Pods

Each Pod has an associated GCS bucket containing datasets and other objects relevant to the Pod. Get a list of currently available Pods by doing:

```{r}
list_pods()
```

This function does not access GCS and therefore does not require an authorisation step.

### See a Research Pod's GCS objects

See all objects associated with a Research Pod:

```{r}
get_pod_meta(pod = "EquityFactors")
```

This function does not access GCS and therefore does not require an authorisation step.

### Kick off an OAuth process to access The Lab's cloud infrastructure

If called in an interactive session, you will be prompted in a browser to select a Google Identity and copy and paste an authentication code back at the call site.

This is useful if you need re-authorise, or if you want to access specific Lab objects in GCS without doing the entire setup process.  

```{r, eval=FALSE, echo=TRUE}
rwlab_gc_auth()
```


### Load all GCS objects for a Research Pod

This transfers all objects associated with a Pod from GCS to `path`, overwriting any existing local Pod objects. 

This is useful if you need a fresh copy of the Pod's datasets, but don't need to re-authorise to GCS. Requires that you've already authorised to the relevant GCS bucket.
 
```{r, eval=FALSE, echo=TRUE}
load_pod_data(pod = "EequityFactors", path = ".")
```

### Load a specific GCS object

This transfers a specifc object from GCS to `path`, overwriting any existing local instance of that object. 

This is useful if you need a fresh copy of a single dataset, but don't need to re-authorise to GCS. Requires that you've already authorised to the relevant GCS bucket.

```{r, eval=FALSE, echo=TRUE}
load_lab_object(path = ".", object = "clean_R1000.csv", bucket = "rw_equity_research_sprint")
```
